Arjun Shanmugam's Senior Thesis

### 2022-12-23 writing/paper/main.tex

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}

@@

\section{Data} \label{sec:data}
    \subsection{Evictions Data}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
    \subsection{Summary Statistics}
        \begin{table}[]
            \centering
            \begin{tabular}{c|c}
                 &  \\
                 & 
            \end{tabular}
            \caption{Caption}
            \label{tab:my_label}
        \end{table}

>>>>

\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}

@@

\section{Data} \label{sec:data}
    \subsection{Evictions Data}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
    \subsection{Summary Statistics}
        \begin{table}[H]
            \centering
            \input{output/summary_statistics/tables/summary_statistics.tex}
            \caption{Caption}
            \label{tab:my_label}
        \end{table}
